The limits of self commitment and private paternalism \thanks{}

### 2021-09-10 donde.tex
Redefine definition of financial cost as effective cost/loan ratio
Former-commit-id: 6ca64d61c64e073a31eb2db5a471af41f2c3e9a6

\title{The limits of self-commitment and private paternalism \thanks{We want to thank Craig McIntosh, Mauricio Romero, and Anett John for advice and encouragement. Ricardo Olivares, Gerardo Melendez, and Alonso de Gortari provided excellent research assistance and Erick Molina helped with formatting. Jose Maria Barrero, Andrei Gomberg, Emilio Gutierrez, David Laibson, Aprajit Mahajan, Matt Rabin, Charlie Sprenger, and seminar participants at ITAM provided valuable feedback.}}
\author{Isaac Meza \and Joyce Sadka \and Enrique Seira   \thanks{Seira: ITAM, enrique.seira@gmail.com (corresponding author); Meza: University of California at Berkeley, isaac.meza@berkeley.edu; Sadka: ITAM, jsadka@itam.mx} }
\date{This draft:  \today \\[2 cm]}

@@

In the context of pawnbroker lending, we show that forcing people into commitment contracts with financial penalties for not paying on time \textit{decreases} their (fee-including) financial cost by 9.4\%, increases the likelihood of recovering their pawn by 26\%, and increases the likelihood of repeat business by almost 100\%. Using machine learning methods for estimating heterogeneous treatment effects, we find that more than \hl{90}\% clients would reduce their financing cost with the commitment contract, however only 10\% choose it. Relying on personal promises instead of fees as commitment triples take-up but has no effects on outcomes.

@@

Many institutions ---firms, schools, financial contracts--- restrict choice using built-in commitment mechanisms which help workers, students, borrowers overcome self-control problems. For instance, ``[mortgages restrict choice] with a fixed repayment stream and mandatory principal repayment'' \citep{Laibson2018}.\footnote{\cite{Laibson2018} also mentions that ``Firms do limit their workers' freedom with intermediate deadlines, progress reports, production targets'', and schools with ``pop quizzes, classroom attendance requirements, cold calling, graded problem sets, deadlines''.} At the same time  these same firms shroud these forcing mechanisms and don't market their commitment features, presumably because students, workers and borrowers ``don't welcome these paternalistic restrictions''. \cite{Laibson2018} argues that this presents an important puzzle: clients that benefit from commitment although may underestimate its value and this have low demand for it. In such a case private paternalism may be beneficial.\footnote{\cite{Laibson2018} defines paternalism as a policy that advances an individual's interests by restricting his or her freedom, and private paternalism as paternalism implemented by private institutions. In this paper we will study the effect of restricting freedom of contract choice on two outcomes: pawn recovery and financing cost, not overall welfare.}

This paper studies the benefits of restricting choice in the context of pawnbroker lending. Pawn loans are one of the oldest, most understudied, and most prevalent forms of borrowing. There are more than 11,000 pawn shops across the US, with 30 million clients and \$14 billion yearly revenues (in China it is a 43 billion dollar industry).\footnote{\url{https://tinyurl.com/ybm56dpe}, \url{https://tinyurl.com/y9zdcgws}, \url{https://tinyurl.com/y59ptdam}.} Our partner pawn lender (henceforth Lender $P$) alone served more than 1 million clients in the last 3 years with more than 4 million contracts.\footnote{For comparison there were 2.3 million micro-finance clients in Mexico in 2009 (\cite{Pedroza:2010}).} The key characteristic of pawn loans is that the borrower leaves personal property (a pawn) as collateral in exchange for an immediate cash loan of a smaller value. In our case Lender $P$ only accepts gold jewelry as collateral and approves all pawns, giving cash the equivalent of 70\% of the pawn's appraised value. The contract stipulates a 7\% monthly interest rate charged daily, a loan term of 90 days, and the flexibility to pay back the loan at anytime before the loan is due. In spite of this flexibility, most people lose their pawn, and among those that recover it almost all of them pay in the last days, just before the loan elapses.\footnote{In the US default is also high at 15\% (\url{https://tinyurl.com/yc2x5bjf}).}

@@

%Borrowers typically turn to these loans when in desperate need to pay for an emergency. The vulnerability of these borrowers has sparked regulator's interest.\footnote{In 2013 Mexico's Consumer Protection Bureau (Profeco) is concerned about abuse. It forced Pawnshops to be more transparent in their pricing, register their contracts with them and issued regulation to protect clients. Congress has enacted laws in this regard. \url{http://www.diputados.gob.mx/LeyesBiblio/ref/lfpc.htm}.} One concern is that borrowers selecting into these loans may exhibit particularly strong behavioral biases. 
%Using a survey conducted by us in branches of Lender $P$, we indeed document some evidence consistent with these concerns: while pawnshop clients predict they will recover their pawn with 93\% probability on average, in reality only 40\% of them do, suggesting naivete. 
%Even conditional on paying a positive amount towards pawn recovery, 53\% lose their pawn and their payment. In our survey 69\% report self-control problems saying they often fall into temptation spending. %, but only \hlgr{15\%} show inter-temporal inconsistencies in a classical present-bias question, a similar number to \cite{Ashaf}. %and \hl{19\%} do not normally budget monthly expenses. 
%While this is suggestive of a present bias problem or overconfidence to save and pay, at the same time our subjects are experienced and not wholly uneducated, 66\% have completed at least high school and 90\% have pawned before. %and \hl{38\%} have participated in a Rosca.

We implemented a large randomized control trial with close to 10,000 pawnshop clients in 6 branches of Lender $P$ in Mexico City. We answer five main questions using this experiment. First, would clients benefit  ---in terms of recovering their pawn and in terms of incurring in lower financing costs---  from having a frequent (monthly) payment commitment contract \textit{forced} on them, instead of the current 3-month pay-when-you-want contract? That is, we are asking whether \textit{charging} them a 2\% late payment fee for not paying a monthly installment on time can actually \textit{decrease} total (fee-inclusive) financing cost. Second, would there be demand for such an installment contract vis-a-vis the status quo one if given choice? Any payment profile implemented in the commitment contract can be replicated by the borrower under the status quo contract, but the former provides commitment. Third, would clients who benefit from commitment the most (e.g. the present biased or overconfident) demand it more? Fourth, are late payment fees key to provide commitment or would a non-pecuniary but salient personal promise to pay provide a cost-reducing mix of commitment vs flexibility? Promises change behavior significantly in laboratory settings, but we know little about their effect in natural environments.\footnote{%Some papers in this space are \cite{PromisesPartnerships}, \cite{Vanberg}, \cite{Belot2010}, \cite{WhyDoPromises}, \cite{FurtherPromises}, \cite{Ismayilov2017}. 
There is some actual policy around using promises for loans: the government Mexico has created a program called ``Loans on your word'' for uncollateralized borrowing (\url{http://tiny.cc/yfmnmz}), but unfortunately there is little information about them.} Finally, is \textit{giving choice} among contracts better than forcing clients into payment-commitment contracts in terms of minimizing financing costs incurred and the likelihood of recovering their pawn? Or on the contrary, is it better to force the installment contract 
paternalistically?

The experiment involved 5 arms, with randomization happening at the branch-day level. It is described in detail in Section \ref{Experiment}. Here let us briefly explain the main 3 arms. The first one involves a group of clients that were given only the status quo contract (henceforth the \textit{status-quo forcing group}). The second arm (\textit{fee-forcing group}) was given a monthly payment commitment contract, which stipulated that clients had to pay 1/3 of their loan plus accumulated interest in each of the 3 months of the term length. Failing to do this would result in a fee of 2\% of the amount due that month. A third group (\textit{Fee-choice group}) gave clients a choice between these two contracts.

Forcing clients into frequent payment commitment contracts causes them on average to save on financing cost and to recover their pawn more. The effects are large: financing cost decreases by 9.4\% on average (from \$3157 to \$2860 MXN), while the likelihood of recovering their pawn increases by 26\% (from 43\% to 55\%). Results are robust qualitatively to including transport costs of going to the branch plus losing a day's wage for each visit. Importantly, the benefits are distributed broadly: almost the whole distribution of treatment effects shows cost savings; however those most economically vulnerable, and notably, those we classify as overconfident, experience larger gains. %The commitment contract also causes payments to start 8 days earlier and be 16\% more frequent, compared to the control group. 
Treatment effects are concentrated in the intensive margin as treatment does not affect the fraction of clients who pay a positive amount towards pawn recovery. The fee-commitment contract induces people who would otherwise pay something towards recovery, to pay more and faster and thus recover their pawn more at a cheaper financial cost. Finally, borrowers assigned to the forced fee-commitment contract are 5 percentage points (100\% of the mean) more likely than the control group to ask for another loan in the future, suggesting that they liked the commitment contract after experiencing it.

@@

In spite of these estimated benefits for almost all clients, actual demand for the fee-commitment contract is low. Only 10\% of the group offered a choice between the monthly payment fee-commitment contract and the status-quo one chose the former. This is not likely driven by misunderstanding the (already simple) contract.\footnote{We posted two project assistants in each of the experimental branches every day for all branch opening hours to carefully explain the contracts; material was developed to explain the differences among the two contracts, and subjects spelled back to our team the loan differences. Furthermore take up is systematically predicted by baseline covariates, making it less likely that these are just random mistakes.} We show further that clients that most benefit from the contract (those who are overconfident about recovering) are \textit{less} likely to demand it, echoing a result by \cite{Sprenger}. %is Low demand for commitment is consistent with a large literature (\cite{Laibson2015}, \cite{Laibson2018}, \cite{John}, \cite{Ted}, \cite{Rabin2018}). 
%\footnote{\cite{Alcohol} and \cite{Kremer} are some of the few instances of high demand for commitment. \cite{Alcohol} speculates that this difference may be explained by their subjects having more experience with their self control problem. Close to ninety percent of our subjects claim to have pawned before. We find that experience does not predict positive take up in our sample.} 
%\cite{Laibson2015} shows that the lost flexibility resulting from a commitment contract can severely limit take-up when agents are naive about their self control, even though commitment could be welfare improving for them. 
Owing to this low take-up, we estimate zero average treatment effects of the \textit{fee-choice} arm on financial cost and on pawn recovery throughout the quantile distribution.

@@

Combining the forcing and the choice arms ---a unique feature of our experiment--- allows us to estimate the counterfactuals to answer the question of how much money is left on the table by giving choice to clients. We calculate that about \hl{80}\% of clients in the fee-choice group chose contracts that induced \textit{higher} financial cost. On average they spend an extra \$\hl{238} MXN, close to \hl{11}\% of the average loan value. In particular \hl{92}\% of those that chose the status-quo contract would have been better in the fee-commitment contract, while only \hl{8}\% of those who chose the fee-commitment contract would have been better in the status-quo one. This suggests that forcing clients into commitment contacts (i.e. private paternalism) may be beneficial for the overwhelming majority of clients. After seeing our results Lender $P$ introduced frequent payment contracts in their loans portfolio.

We want to clarify that in the paper we are using the word ``paternalism'' in a restricted sense, meaning only that a large majority of clients would incur in lower financial costs from being forced into installment contracts instead of letting them choose. We are not making claims about overall welfare which is a slippery concept if we take into account the possibility of biased beliefs and preferences.

Inspired by a significant lab experiment literature on the effects of promises on behavior, and by research showing that a small fee could drastically reduce demand for commitment of (partly) naive present-biased borrowers (\cite{Laibson2015}), we implemented a ``psychological commitment'' in the form of a salient promise to pay.  \cite{PromisesPartnerships}, \cite{FurtherPromises}, \cite{Vanberg}, and \cite{Ismayilov2017} find that the ability to make a promise about behaving a certain way makes the individual more likely to adhere to the promised behavior. %and also induces trusting behavior by the recipients of the promise. 
To measure the causal effect of promises we implemented two other treatment arms. A \textit{promise-forcing} arm exactly analogous to our \textit{fee-forcing arm} except that instead of telling them that there was a fee if they didn't pay on time, we made borrowers promise that they would pay one third of the amount in each of the 3 months, and told them that if they didn't they would have broken their promise and not kept their word. Because salience is key we made them sign a (legally non-binding) personal promise and emphasized that we were counting on them to keep their promise. A final arm (\textit{promise-choice arm}) gave clients the opportunity to choose between the \textit{Promise} contract and the \textit{Status-quo} contract.

We document two main results in the promise arms. First, demand for the commitment-promise contract is three times larger than for the commitment fee contract, with \hl{31}\% take-up. This difference between both choice arms suggests that clients are indeed understanding and taking into account the contractual parameters in their choice, and that the fee commitment was probably too strong from their point of view. In spite of this much higher take-up, the \textit{Promise-choice arm} had no effect on outcomes on average, or even for those who selected into promising. Second, being forced in to the \textit{Promise} contract also had zero effects on average and throughout the distribution on financing cost and pawn recovery. %\footnote{There is a decrease in financial cost in the 50th and 75th quantiles in the forced promise-commitment arm however.}
Promises did not provide enough commitment so as to be reflected in behavior.

This paper contributes to several strands of literature. First, we focus on an important new context: pawnshop borrowing. Pawnshop borrowing is extremely prevalent in developing countries and very worrisome to regulators, yet severely understudied.\footnote{The World Bank's CGAP recognizes the importance of pawnshop borrowing worldwide but provides no statistics or analysis on it (\url{https://tinyurl.com/ydgob8pv}). We could not find peer-reviewed papers about it either.} It is different from microfinance in that it deals with emergency loans, and not loans for productive investment. Because of this, it may draw on a more vulnerable (and potentially more unsophisticated) population. Moreover, the trade-off between loan rigidity and investment found for microfinance \citep{Field} may not be there for pawn borrowing.  Second, a significant literature has shown that demand for commitment exists but is somewhat low in some contexts (\cite{Ashraf}, \cite{Gine}, \cite{Ted}, \cite{Royer}, \cite{Sprenger}), and high in others (\cite{Kremer},  \cite{Casaburi}, \cite{Alcohol}, \cite{AprajitP&P}, \cite{Pascaline}). We add to this literature by showing --although we may not be the only ones-- that very small fees\footnote{For instance our fees are 16 times smaller than than those of \cite{John} as a fraction of the loan/goal, and 5 times smaller converting peso values using exchange rates.} are enough to drastically reduce demand for commitment, even when commitment is cost-reducing. We also show that softer commitments in the form of non-pecuniary personal promises elicit higher demand but do not affect behavior or financing costs.

Third, \cite{John} and \cite{Ted} show that the extent of commitment needed is underestimated even among those that purchase commitment mechanisms, and that subjects hurt themselves by self-imposing too weak a commitment in the intensive margin. We contribute in design by not allowing choice of the extent of commitment, and methodologically by inferring subjects underestimation of the value of commitment ex-ante from forgone treatment savings, instead of from subjects failing to reach a goal ex-post. In consonance with \cite{Sprenger} but in our very different context, we find that people who most need commitment (in our case the overconfident, as they have the larger treatment effects) are also the ones less likely to demand it when given choice. In contrast to \cite{Sprenger}, our context allows us to focus on money savings instead of estimated utility to proxy for benefits of commitment, a narrower but more transparent measure. This allows us to measure effects on cost outcomes beyond take up. As in \cite{Rabin2018} we are able to contrast subjects' \textit{own predictions} of their behavior with their actual behavior, and how these map to outcomes, but we do it in a natural setting.

Fourth, and most importantly, we study both causal effects and selection into frequent payment commitment loan contracts at the same time and for the same population in a single experiment. We know of no other experiment in the credit market which simultaneously combines forcing and choice arms. This feature, when paired with new machine learning methods to estimate heterogeneous treatment effects (\cite{atheygrf}), allows us to show whether there is positive or negative selection into beneficial contracts, and whether pawnshop clients forego money by not demanding commitment. In consonance with what \cite{Walters} finds in the school choice context, we find that it is \textit{not}  those who benefit most from the contract that demand it more.

Studying causal effects of installment payment frequency, \cite{Pande} find null effects on loan default, a surprising result given the prevalence of frequent payment contracts. In contrast we find strong effects of payment frequency on decreased default.\footnote{There are many differences in context between the papers which may explain the different result. \cite{Pande} focus on group lending with very little default to start with (less than 1\%), while in our case almost half of loans end in default. We also have a larger sample and we focus on individualized loans, which may afford us stronger statistical power to detect effects.} Our result is consistent with \cite{Field} who show that delaying payment in microfinance loans increases default.\footnote{\cite{Craig} use the discipline of regular loan repayments in microfinance to remind people to save and make a savings plan, and find large increases in savings.} On the other hand, studying selection into frequent payment microfinance loans, \cite{Murdoch} show that a robust positive correlation exists between displaying present biased preferences in surveys and selecting into microfinance, which they interpret as being due to high demand for the discipline imposed by frequent payments. However they acknowledge that this ``interpretation is suggestive... and needs to be confirmed by studies that establish causal links''. Our experiment is a test of this causal link, and it rejects the hypothesis that the majority of microfinance (pawnshop) clients demand frequent payments contracts, at least in our context.

@@

Finally, even though personal promises feature prominently in microfinance guidelines\footnote{e.g. \url{https://grameenfoundation.org/documents/GrameenGuidelines.pdf}, p.36.} we know of no other study that has tried to isolate their effects on loan repayment.  In concordance with this literature we find that people are willing and indeed voluntarily choose to make promises. We find however that measured behavior was unchanged by promising.\footnote{This is of course not a refutation of this literature by any means. %not least because the laboratory literature is implemented on more tightly controlled environments and focused on subtler aspects of promising, like their effects on second order beliefs and guilt aversion. The context is also different since 
The lab literature has focused mostly on very structured investment games between two players and looked at the effects of promises on trust and cooperation through guilt aversion and cost of lying channels. In our case the bank is not a strategic player that responds to the promise or a person (although the teller is). However, our results do provide a first piece of evidence on the limitations of using promises to change behavior in loan contracts.}

@@

Table \ref{SS} presents some summary statistics for the whole sample and by treatment arm. Because treatment arms are described below, here we concentrate on the overall average. Panel A describes variables from the administrative data. The average loan size is \$2197 MXN (\$105 USD). The average number of pawns per day per branch is 34. Only 42\% of clients recover their pawn within 230 days. Even those that recover their pawn tend to pay it back at the last moment, with only 40\% paying before the 90th day.

>>>>

\title{The limits of self-commitment and private paternalism \thanks{We want to thank Mauricio Romero and Anett John for advice and encouragement. Ricardo Olivares, Gerardo Melendez, and Alonso de Gortari provided excellent research assistance and Erick Molina helped with formatting. Jose Maria Barrero, Andrei Gomberg, Emilio Gutierrez, David Laibson, Aprajit Mahajan, Matt Rabin, Charlie Sprenger, and seminar participants at ITAM provided valuable feedback.}}
\author{Craig McIntosh \and Isaac Meza \and Joyce Sadka \and Enrique Seira   \thanks{Seira: ITAM, enrique.seira@gmail.com (corresponding author); Meza: University of California at Berkeley, isaac.meza@berkeley.edu; Sadka: ITAM, jsadka@itam.mx} }
\date{This draft:  \today \\[2 cm]}

@@

In the context of pawnbroker lending, we show that forcing people into commitment contracts with financial penalties for not paying on time \textit{decreases} their (fee-including) financial cost by 9.4\%, increases the likelihood of recovering their pawn by 26\%, and increases the likelihood of repeat business by almost 100\%. Using machine learning methods for estimating heterogeneous treatment effects, we find that more than {70}\% clients would reduce their financing cost with the commitment contract, however only 10\% choose it. Those that \textit{don't} choose it are predicted to be the ones who would benefit more. Relying on personal promises instead of fees as commitment triples take-up but has no effects on outcomes.

@@

Many institutions ---firms, schools, financial contracts--- restrict choice using built-in commitment mechanisms which help workers, students, borrowers overcome self-control problems. For instance, ``[mortgages restrict choice] with a fixed repayment stream and mandatory principal repayment'' \citep{Laibson2018}.\footnote{\cite{Laibson2018} also mentions that ``Firms do limit their workers' freedom with intermediate deadlines, progress reports, production targets'', and schools with ``pop quizzes, classroom attendance requirements, cold calling, graded problem sets, deadlines''.} At the same time  these same firms shroud and don't market these commitment features, presumably because students, workers and borrowers don't welcome these restrictions. \cite{Laibson2018} argues that this presents an important puzzle: clients that would benefit from commitment underestimate its value and thus have low demand for it. In such a case private paternalism may be beneficial.\footnote{Laibson defines paternalism as a policy that advances an individual's interests by restricting his or her freedom, and private paternalism as paternalism implemented by private institutions. %In this paper we will study the effect of restricting freedom of contract choice on two outcomes: pawn recovery and financing cost, not overall welfare.
We want to clarify that we are using the word ``paternalism'' in a restricted sense, meaning only that a large majority of clients would incur in lower financial costs from being forced into installment contracts instead of letting them choose. We are not making claims about overall welfare which is a slippery concept if we take into account the possibility of biased beliefs and preferences.}

This paper studies the benefits of restricting choice in the context of pawnbroker lending. Pawn loans are one of the oldest, most understudied, and most prevalent forms of borrowing. There are more than 11,000 pawn shops across the US, with 30 million clients and \$14 billion yearly revenues. In China it is a 43 billion dollar industry.\footnote{\url{https://tinyurl.com/ybm56dpe}, \url{https://tinyurl.com/y9zdcgws}, \url{https://tinyurl.com/y59ptdam}.} Our partner pawn lender (henceforth Lender $P$) alone served more than 1 million clients in the last 3 years with more than 4 million contracts. The key characteristic of pawn loans is that the borrower leaves personal property (a pawn) as collateral in exchange for an immediate cash loan of a smaller value. In our case Lender $P$ only accepts gold jewelry as collateral and approves all pawns, giving cash the equivalent of 70\% of the pawn's appraised value. The contract stipulates a 7\% monthly interest rate charged daily, a loan term of 90 days, and the flexibility to pay back the loan at anytime before the loan is due. In spite of this flexibility ---or perhaps because of it--- 60\% of clients lose their pawn\footnote{In the US default is also high at 15\% (\url{https://tinyurl.com/yc2x5bjf}).}, and among those that recover it almost all of them pay in the days just before the loan elapses.

@@

%Borrowers typically turn to these loans when in desperate need to pay for an emergency. The vulnerability of these borrowers has sparked regulator's interest.\footnote{In 2013 Mexico's Consumer Protection Bureau (Profeco) is concerned about abuse. It forced Pawnshops to be more transparent in their pricing, register their contracts with them and issued regulation to protect clients. Congress has enacted laws in this regard. \url{http://www.diputados.gob.mx/LeyesBiblio/ref/lfpc.htm}.} One concern is that borrowers selecting into these loans may exhibit particularly strong behavioral biases. 
%Using a survey conducted by us in branches of Lender $P$, we indeed document some evidence consistent with these concerns: while pawnshop clients predict they will recover their pawn with 93\% probability on average, in reality only 40\% of them do, suggesting naivete. 
%Even conditional on paying a positive amount towards pawn recovery, 53\% lose their pawn and their payment. In our survey 69\% report self-control problems saying they often fall into temptation spending. %, but only gr{15\%} show inter-temporal inconsistencies in a classical present-bias question, a similar number to \cite{Ashaf}. %and {19\%} do not normally budget monthly expenses. 
%While this is suggestive of a present bias problem or overconfidence to save and pay, at the same time our subjects are experienced and not wholly uneducated, 66\% have completed at least high school and 90\% have pawned before. %and {38\%} have participated in a Rosca.

We implemented a large randomized control trial with close to 10,000 pawnshop clients in 6 branches of Lender $P$ in Mexico City. We answer five main questions using this experiment. First, would clients benefit  ---in terms of recovering their pawn and in terms of incurring in lower financing costs---  from having a frequent (monthly) payment commitment contract \textit{forced} on them, instead of the current 3-month pay-when-you-want contract? That is, we are asking whether \textit{charging} them a 2\% late payment fee for not paying a monthly installment on time can actually \textit{decrease} total (fee-inclusive) financing cost. Second, would there be demand for such an installment contract vis-a-vis the status quo one if given the choice? Note that any payment profile implemented in the commitment contract can be replicated by the borrower under the status quo contract, but the former provides commitment. Third, would clients who benefit from commitment the most (e.g. the present biased or overconfident) demand it more? Fourth, are late payment fees key to provide commitment or would a non-pecuniary but salient personal promise to pay provide a cost-reducing mix of commitment vs flexibility? Promises change behavior significantly in laboratory settings, but we know little about their effect in natural environments.\footnote{%Some papers in this space are \cite{PromisesPartnerships}, \cite{Vanberg}, \cite{Belot2010}, \cite{WhyDoPromises}, \cite{FurtherPromises}, \cite{Ismayilov2017}. 
There is some actual policy around using promises for loans: the government Mexico has created a program called ``Loans on your word'' for uncollateralized borrowing (\url{http://tiny.cc/yfmnmz}), but unfortunately there is little information about them.} Finally, is \textit{giving choice} among contracts better than forcing clients into payment-commitment contracts in terms of minimizing financing costs incurred and the likelihood of recovering their pawn? Or on the contrary, is it better to force the installment contract 
paternalistically?

The experiment involved 5 arms, with randomization happening at the branch-day level. It is described in detail in Section \ref{Experiment}. Here let us briefly explain the main 3 arms. The first one involves a group of clients that were given only the status quo flexible payments contract (henceforth the \textit{status-quo forcing group}). The second arm (\textit{fee-forcing group}) was given a monthly payment commitment contract, which stipulated that clients had to pay 1/3 of their loan plus accumulated interest in each of the 3 months of the term length. Failing to do this would result in a fee of 2\% of the amount due that month. A third group (\textit{Fee-choice group}) gave clients a choice between these two contracts.

Results are striking. First, we find that forcing clients into frequent payment commitment contracts causes them on average to save on financing cost and to recover their pawn more. The effects are large: financing cost decreases by 9.4\% on average (from \$3157 to \$2860 MXN), while the likelihood of recovering their pawn increases by 26\% (from 43\% to 55\%). Results are robust qualitatively to including transport costs of going to the branch plus losing a day's wage for each visit. Importantly, the benefits are distributed broadly: almost the whole distribution of treatment effects shows cost savings; however those most economically vulnerable, and notably, those we classify as overconfident, experience larger gains. %The commitment contract also causes payments to start 8 days earlier and be 16\% more frequent, compared to the control group. 
Treatment effects are concentrated in the intensive margin as treatment does not affect the fraction of clients who pay a positive amount towards pawn recovery. That is, the fee-commitment contract induces people who would otherwise pay something towards recovery, to pay more and faster and thus recover their pawn more at a cheaper financial cost. Finally, borrowers assigned to the forced fee-commitment contract are 5 percentage points (100\% of the mean) more likely than the control group to ask for another loan in the future, suggesting that they liked the commitment contract after experiencing it.

@@

Second, in spite of these estimated benefits for almost all clients, actual demand for the fee-commitment contract is low. Only 10\% of the group offered a choice between the monthly payment fee-commitment contract and the status-quo one chose the former. This is not likely driven by misunderstanding the (already simple) contract.\footnote{We posted two project assistants in each of the experimental branches every day for all branch opening hours to carefully explain the contracts; material was developed to explain the differences among the two contracts, and subjects spelled back to our team the loan differences. Furthermore take up is systematically predicted by baseline covariates, making it less likely that these are just random mistakes.} We show further that clients that most benefit from the contract (those who are overconfident about recovering) are \textit{less} likely to demand it, echoing a result by \cite{Sprenger} for grocery purchases and \cite{Walters} for schools. %is Low demand for commitment is consistent with a large literature (\cite{Laibson2015}, \cite{Laibson2018}, \cite{John}, \cite{Ted}, \cite{Rabin2018}). 
%\footnote{\cite{Alcohol} and \cite{Kremer} are some of the few instances of high demand for commitment. \cite{Alcohol} speculates that this difference may be explained by their subjects having more experience with their self control problem. Close to ninety percent of our subjects claim to have pawned before. We find that experience does not predict positive take up in our sample.} 
%\cite{Laibson2015} shows that the lost flexibility resulting from a commitment contract can severely limit take-up when agents are naive about their self control, even though commitment could be welfare improving for them. 
Owing to this low take-up, we estimate zero average treatment effects of the \textit{fee-choice} arm on financial cost and on pawn recovery throughout the quantile distribution.

@@

Third, combining the forcing and the choice arms ---a unique feature of our experiment--- allows us to estimate the counterfactuals to answer the question of how much money is left on the table by giving choice to clients. We calculate that about {80}\% of clients in the fee-choice group chose contracts that induced \textit{higher} financial cost. On average they spend an extra \${238} MXN, close to {11}\% of the average loan value. In particular {92}\% of those that chose the status-quo contract would have been better in the fee-commitment contract, while only {8}\% of those who chose the fee-commitment contract would have been better in the status-quo one. This suggests that forcing clients into commitment contacts ---private paternalism--- may be beneficial for the overwhelming majority of clients. After seeing our results Lender $P$ introduced frequent payment contracts in their loans portfolio.

Inspired by a significant lab experiment literature on the effects of promises on behavior, and by research showing that a small fee could drastically reduce demand for commitment of (partly) naive present-biased borrowers (\cite{Laibson2015}), we implemented a ``psychological commitment'' product in the form of a salient promise to pay.  \cite{PromisesPartnerships}, \cite{FurtherPromises}, \cite{Vanberg}, and \cite{Ismayilov2017} find that the ability to make a promise about behaving a certain way makes the individual more likely to adhere to the promised behavior. %and also induces trusting behavior by the recipients of the promise.

To measure the causal effect of promises we implemented two other treatment arms. A \textit{promise-forcing} arm exactly analogous to our \textit{fee-forcing arm} except that instead of telling them that there was a fee if they didn't pay on time, we made borrowers promise that they would pay one third of the amount in each of the 3 months, and told them that if they didn't they would have broken their promise and not kept their word. Because salience is key we made them sign a (legally non-binding) personal promise and emphasized that we were counting on them to keep their promise. A final arm (\textit{promise-choice arm}) gave clients the opportunity to choose between the \textit{Promise} contract and the \textit{Status-quo} contract.

We document three main results in the promise arms. First, demand for the promise-commitment contract is three times larger than for the fee-commitment contract, with {31}\% take-up. This difference shows that clients are indeed taking into account the contractual parameters when they choose, and that the fee commitment was probably too strong from their point of view. Second, in spite of this much higher take-up, the \textit{Promise-choice arm} had no effect on outcomes on average, or even for those who selected into promising. Third, being forced in to the \textit{Promise} contract also had zero effects on average and throughout the distribution on financing cost and pawn recovery. %\footnote{There is a decrease in financial cost in the 50th and 75th quantiles in the forced promise-commitment arm however.}
Promises did not provide enough commitment so as to be reflected in behavior. This is one of the first  experiments using promises in the field, and results are in striking contrast with those in the lab.

This paper contributes to several strands of literature. First, we focus on an important new context: pawnshop borrowing. Pawnshop borrowing is extremely prevalent in developing countries and very worrisome to regulators, yet severely understudied.\footnote{The World Bank's CGAP recognizes the importance of pawnshop borrowing worldwide but provides no statistics or analysis on it (\url{https://tinyurl.com/ydgob8pv}). We could not find peer-reviewed papers about it either.} It is different from microfinance in that it deals with emergency loans, and not loans for productive investment. Because of this, it may draw on a more vulnerable (and potentially more unsophisticated) population, and because it is not typically used for productive investment, the trade-off between loan rigidity and investment found for microfinance \citep{Field} may not be there.

Second, a significant literature has shown that demand for commitment exists. But while it is low in some contexts (\cite{Ashraf}, \cite{Gine}, \cite{Ted}, \cite{Royer}, \cite{Sprenger}), it is high in others (\cite{Kremer},  \cite{Casaburi}, \cite{Alcohol}, \cite{AprajitP&P}, \cite{Pascaline}). We add to this literature by adding evidence from another market. Demand for commitment  is low, and very small fees\footnote{For instance our fees are 16 times smaller than than those of \cite{John} as a fraction of the loan/goal, and 5 times smaller converting peso values using exchange rates.} are enough to drastically reduce demand for commitment, even when commitment is cost-reducing. Softer commitment contracts in the form of promises do increase demand but did not change outcomes. %We also show that softer commitments in the form of non-pecuniary personal promises elicit higher demand but do not affect behavior or financing costs.

Third, and most importantly, we study both causal effects and selection into frequent payment commitment loan contracts at the same time and for the same population in a single experiment. We know of no other experiment in the credit market which simultaneously combines forcing and choice arms. This feature, when paired with new machine learning methods to estimate heterogeneous treatment effects \citep{atheygrf}, allows us to show whether there is positive or negative selection into beneficial contracts, and whether pawnshop clients forego money by not demanding commitment. In consonance with what \cite{Walters} finds in the school choice context, we find that it is \textit{not} those who benefit most from the contract that demand it more.  \cite{Sprenger} find similar result in the context of grocery purchases. In contrast to \cite{Sprenger}, our context allows us to focus on money savings instead of estimated utility to proxy for benefits of commitment, a narrower but more transparent measure. This allows us to measure effects on cost outcomes beyond take up.\footnote{\cite{John} and \cite{Ted} show that the extent of commitment needed is underestimated. In contrast to them, we infer subjects underestimation of the value of commitment from their forgone treatment savings, instead of from subjects failing to reach a goal.}

%Third, in consonance with \cite{Sprenger} and \cite{Walters} but in our very different context, we find that people who most need commitment (in our case the overconfident, as they have the larger treatment effects) are also the ones less likely to demand it when given choice.

Fourth, we provide new evidence on the payment frequency debate. The literature has found null effects on installment frequency loan default \cite{Pande}. This result is at odds with the prevalence of frequent payment contracts in markets. We find strong effects of payment frequency on decreased default.\footnote{There are many differences in context between the papers which may explain the different result. \cite{Pande} focus on group lending with very little default to start with (less than 1\%), while in our case almost half of loans end in default. We also have a larger sample and we focus on individualized loans, which may afford us stronger statistical power to detect effects.} Our result is consistent with \cite{Field} who show that delaying payment in microfinance loans increases default.\footnote{\cite{Craig} use the discipline of regular loan repayments in microfinance to remind people to save and make a savings plan, and find large increases in savings.}

We believe that taken together, our results (commitment matters, small fees have large effects on behavior, people don't choose the cost reducing contract) call for a behavioral explanation. Most of the literature tries to connect commitment problems with measures present biased preferences. Results are mixed, which is not surprising given how hard is to measure present bias naivete for instance. Instead of trying to measure those we focus on measuring biased predictions about payment, what we call overconfidence. Not only is it easier to measure, but also more general in the sense of being implied by present bias but not conversely. As in \cite{Rabin2018} we contrast subjects' \textit{own predictions} of their behavior with their actual behavior, but we do it in a natural setting. \cite{Murdoch} show that a robust positive correlation exists between displaying present biased preferences in surveys and selecting into microfinance, which they interpret as being due to high demand for the discipline imposed by frequent payments. However they acknowledge that this ``interpretation is suggestive... and needs to be confirmed by studies that establish causal links''. Our experiment is a test of this causal link.

@@

Finally, even though personal promises feature prominently in microfinance guidelines\footnote{e.g. \url{https://grameenfoundation.org/documents/GrameenGuidelines.pdf}, p.36.} we know of no other study that has tried to isolate their effects on loan repayment.  In concordance with this literature we find that people are willing and indeed voluntarily choose to make promises. We find however that measured behavior was unchanged by promising.\footnote{This is of course not a refutation of the laboratory literature. %not least because the laboratory literature is implemented on more tightly controlled environments and focused on subtler aspects of promising, like their effects on second order beliefs and guilt aversion. The context is also different since 
The lab literature has focused on very structured investment games between two players and looked at the effects of promises on trust and cooperation. In our case the bank is not a strategic player that responds to the promise, or a person to which the client can feel guilt towards (although the teller is). However, our results do provide a first piece of evidence on the limitations of using promises to change behavior in loan contracts.}

@@

Table \ref{SS} presents some summary statistics for the whole sample and by treatment arm. Because treatment arms are described below, here we concentrate on the overall average. Panel A describes variables from the administrative data. The average loan size is \$2197 MXN (\$105 USD). The average number of pawns per day per branch is 34. Only 42\% of clients recover their pawn. Even those that recover their pawn tend to pay it back at the last moment, with only 40\% paying before the 90th day.
